The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
add to discussion

%We *will* provide 
%spectrophotometric distances based on our stellar parameters, which should 
%be superior to the parallax-based distances for faint or distant objects in
%\tgas.

@@

\subsection{Spectrophotometric distances}
\label{sec:distances}

\stub{These will be derived by Jason Sanders when he returns from his honeymoon.
The timing means that the distances will not be available when we submit the first
version to arXiv. So we may need to remove this section and the reference to it
from the abstract.}

@@

We have presented an independent re-analysis of \rave\ spectra that makes near-maximal
use of the information content for red giant branch stars, and provides a significant
improvement in stellar parameters ($\teff$, $\logg$, [Fe/H]) over previous \rave\ data
releases.  When combined with the \tgas\ sample, these results may amount to a powerful
compendium for chemo-dynamic studies of the Milky Way.  However, our analysis has caveats.
Any inferences based upon these results should be made with the recognition of those caveats,
and acknowledge that they are subject to our explicit assumptions, some of which are 
provably incorrect.

\stub{assumptions that are provably wrong: accurate labels in the training set. lol}

@@

If we only consider the results from individual models, there are a number of cautionary
remarks that stem from the construction of the training set.  The labels for red giant 
branch stars primarily come from \apogee, where previous successes with \thecannon\
have demonstrated that \apogee\ labels based on high S/N data can be of high fidelity.
However, the lack of metal-poor stars in the \apogee/\rave\ overlap sample produced
a tapering-off in the test set, where \emph{no} stars had reliably reported metallicities
below that of the training set, which forced us to construct a heterogeneous training
set.  The metal-poor stars included in this sample are from high-resolution studies
\citep{Fulbright,Ruchti,elsewhere}, but it is unknown if the stellar parameters are
of high fidelity (e.g., we have limited quality metrics available), and there is no
guarantee that the stellar parameters \emph{or} abundances are on the same scale as
\apogee\ \citep[and good reasons to believe they will not be; see][]{Smiljanic_2014}.

\stub{Metallicities on the main-sequence and giant branch -- we cannot be sure if they
are correct. Are there any indications that we can get which suggest whether they are
good or bad?}

For some of the most metal-poor giant stars in \rave\, we \emph{know} the abundances 
are not on the same scale as \apogee, because we were forced to adopt abundances for 
specific elements when they were unavailable.  Although we sought to adopt the mean
level of Galactic chemical enrichment at the overall metallicity, this is not a
representative abundance. Even if that is the \emph{mean} enrichment at that Galactic
metallicity, there is no requirement for zero abundance spread.
More fundamentally, we are incorrectly assuming that the element \emph{must} be 
detectable in the photosphere of the star.  There may be no transition that is 
detectable in that star, even with zero noise, because it is too weak to have any 
effect on the spectrum.  In the most optimistic case, this can be considered to be
forcing the model to make use of correlated information between abundances.  In a
more representative (pessimistic) case, we are simply invoking what all abundances
should be at low metallicity.

@@

\stub{assumptions that are provably wrong: RAVE spectral resolution}

\stub{assumptions that are provably wrong: correlated noise in the RAVE spectra -- this is minor and unlikely to cause a real issue}

@@

@@

>>>>

@@

@@

We have presented an independent re-analysis of \rave\ spectra that makes near-maximal
use of the information content for red giant branch stars, and provides a significant
improvement in stellar parameters ($\teff$, $\logg$, [Fe/H]) over previous \rave\ data
releases.  When combined with the \tgas\ sample, these results may amount to a powerful
compendium for chemo-dynamic studies of the Milky Way.  However, our analysis has caveats.
Inferences based on these results should recognize those caveats, and acknowledge that 
these results are subject to our explicit assumptions, some of which are provably
incorrect.

@@

If we only consider the results from individual models, there are a number of cautionary
remarks that stem from the construction of the training set.  The labels for red giant 
branch stars primarily come from \apogee, where previous successes with \thecannon\
have demonstrated that \apogee\ labels based on high S/N data can be of high fidelity
\citep{Ness_2015,Ness_2016,Ho_2016,Casey_2016}.
However, the lack of metal-poor stars in the \apogee/\rave\ overlap sample produced
a tapering-off in the test set --- where \emph{no} stars had reliably reported metallicities
below that of the training set --- which forced us to construct a heterogeneous training
set.  The metal-poor stars included in this sample are from high-resolution studies
\citep{Fulbright_2010,Ruchti_2011}, but it is unknown if the stellar parameters are
of high fidelity (e.g., we have limited quality metrics available), and there is no
guarantee that the stellar parameters \emph{or} abundances are on the same scale as
\apogee\ \citep[and good reasons to believe they will not be; see][]{Smiljanic_2014}.

If the metallicities of metal-poor giant stars are on the same scale as the \apogee\
abundances, there is a larger issue in verifying that the main-sequence metallicities
and giant branch metallicities are on the same scale.  The training set for the
main-sequence stars includes metallicities from a variety of sources --- including
\lamost, and the fourth \rave\ data release.  Even on expectation value, there is 
no straightforward manner to ensure that these two models produce metallicities on
the same scale.  We see no systematic offset in metallicities of dwarf and giant
stars that overlap between \rave\ and the \ges\ survey, and our examination of
globular and open clusters suggests that \stub{if there is a systematic offset, it must
be small.} Nevertheless, these are only verification checks based on $<1$\% of the
data, and there is currently insufficient data for us to prove both models are on
the same abundance scale.

For some of the most metal-poor giant stars in \rave\, we \emph{know} the abundances 
are not on the same scale as \apogee, because we were forced to adopt abundances for 
specific elements when they were unavailable.  In that sense, our assumption that the
training set contains accurate labels is clearly untrue (for \emph{at least} some stars).
Although we sought to adopt the mean
level of Galactic chemical enrichment at the overall metallicity, this is not a
representative abundance. Even if that is the \emph{mean} enrichment at that Galactic
metallicity, there is no requirement for zero abundance spread.
More fundamentally, we are incorrectly assuming that the element \emph{must} be 
detectable in the photosphere of the star.  There may be no transition that is 
detectable in that star, even with zero noise, because it is too weak to have any 
effect on the spectrum.  In the most optimistic case, this can be considered to be
forcing the model to make use of correlated information between abundances.  In a
more representative (pessimistic) case, we are simply invoking what all abundances
should be at low metallicity.

@@

In Section~\ref{sec:method} we assumed that any fibre- or time-dependent variations
in the \rave\ spectra are negligible.  This is provably incorrect. Indeed,
\citet{Kordopatis_2013} note that the effective resolution of \rave\
spectra varies from $6{,}500 < \mathcal{R} < 8{,}500$, and that the 
effective resolution is a function of time and position on the CCD (e.g., fibre number).  For this reason we ought to expect our derived stellar
parameters or abundances to be correlated with the fibre number, or over
time.  If significant, the trend could produce systematically offset
stellar abundances solely due to the fibre number.  We have not seen
evidence of these correlations in our results, however, we have only
performed cursory (non-exhaustive) experiments to investigate this issue.

@@

\bibitem[Fulbright et al.(2010)]{Fulbright_2010} Fulbright, J.~P., Wyse, R.~F.~G., Ruchti, G.~R., et al.\ 2010, \apjl, 724, L104

@@

\bibitem[Ruchti et al.(2011)]{Ruchti_2011} Ruchti, G.~R., Fulbright, J.~P., Wyse, R.~F.~G., et al.\ 2011, \apj, 743, 107
